The paper on \Large \bf Blockchain Frontrunning

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] some notes

Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions. Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them. We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models. Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial. Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place. In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues. While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.

@@

\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.  The idea of front-running was originated back in stock markets. In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock. This problem occurs when a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders
Nowadays, there are a wide range of decentral applications implemented on the blockchain. Built on the blockchain infrastructure, there is no trusted third party within any of the decentralized applications and there is no central version of information that is vulnerable to security attacks. However, due to the inherent nature of the blockchain data structure, these applications are open to what is called \emph{front-running}. One such application is \textbf{Bancor} -- an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. Researchers have shown that this financial blcokchain application is open to a simple front-running attack.  However, front-running vulnerability is not limited to the financial application and it can happen in other types of blockchain applications as well.

@@

As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection. There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}}.

@@

@@

>>>>

Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions. Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them. We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models. Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial. Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running} losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place. In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues. While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.

@@

\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades.  The idea of front-running was originated back in stock markets. In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock. This problem occurs when a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders
Nowadays, there are a wide range of decentral applications implemented using blockchain technology. Being decentralized, there is no central version of information to be attacked, however, due to the inherent nature of the blockchain infrastructure, the data flow is transparent hence these applications are open to \emph{front-running} attacks. One such application is \textbf{Bancor} -- an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. Researchers have shown that this financial blockchain application is open to a simple front-running attack.  However, front-running vulnerability is not limited to the financial application and it can happen in other types of blockchain applications as well.

@@

As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection. There is no perfect criteria to list top DApps on Ethereum blockchain, for the purpose of this research we analyzed the top 25 DApps based on recent user activities\footnote{List of decentralized applications \url{https://dappradar.com/dapps}}. 
%ICO is only in use when the time window is happenig.  this is based on the last 24hours activities 
%justify why started with ICO and go to other apps

@@

% Talk about how cryptokitties are similar to any other auctions .

@@

%TODO: inline talk about what these solutions are good for and if they fit Status ICO
